formula1

### 2020-06-07 inst/f1points.Rmd
more work

```{r,cache=TRUE}
set.seed(1)
f2017 <- read.table("formula1_2017.txt",header=TRUE)[,1:20]
random_table <- rrank(n=ncol(f2017), p=mH)
rownames(random_table) <- colnames(f2017)
Hran <- ordertable2supp(ranktable_to_ordertable(random_table))
m <- maxp(Hran)
sort(m,decreasing=TRUE)
m[] <- seq_along(m)
m
p <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
dp <- ordertable2points(as.ordertable(ranktable_to_ordertable(random_table)),p)
dp <- sort(dp,decreasing=TRUE)
dp[] <- seq_along(dp)
dp
ox <- dp
oy <- ordertrans(m,dp)
par(pty="s")
plot(1:10,1:10,asp=1,type="p",pch=NA,
    xlab="official order",ylab="my order",main='Formula 1, 2017 virtual season',
	xlim=c(0,11.2),ylim=c(0,11.2))
points(ox,oy,pch=16)
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray') }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)
```

>>>>

```{r,montecarlofirst,cache=TRUE}
top <- 11
f2017 <- read.table("formula1_2017.txt",header=TRUE)[seq_len(top),1:20]
m <- maxp(ordertable2supp(as.ordertable(f2017)))

## Now work on synthetic dataset generation:
points <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
resampling <- function(m,f2017,points){
    random_table <- rrank(n=ncol(f2017), p=m)
    rownames(random_table) <- colnames(f2017)
    ## "random_table" is a random table; now calculate lstar and pstar for
    ## likelihood ranks and points ranks respectively:

    l_star <- maxp(ordertable2supp(ranktable_to_ordertable(random_table)))
    l_star[] <- seq_along(l_star)
    ## l_star is the likelihood order statistic.

    p_star <- ordertable2points(as.ordertable(ranktable_to_ordertable(random_table)),p)
    p_star <- sort(p_star,decreasing=TRUE)
    p_star[] <- seq_along(p_star)

    goodness <- sum(cumprod(names(p_star)==names(l_star)))
    return(goodness)
}

o <- replicate(1000,resampling(m,f2017,points))
plot(table(o))
```
